\documentclass[]{report}
\usepackage{graphicx}
\usepackage{bookmark}

% Title Page
\title{Yavin 4 Defence System}
\author{Grant Louat}


\begin{document}
\maketitle

\begin{abstract}
Welcome to the Yavin 4 Defence System, the premier low cost automatic death star tracker in the 
\end{abstract}

\chapter{Product Description}
\section{Overview}
The Yavin 4 Defence System is a fully automated Death Star Tracker available to rebel republics for a reasonable price. 

\section{Functionality}
The Yavin 4 Defence System includes the following functionality:

\begin{itemize}
	\item Local and Remote User Interface modes
	\item Fully automatic or manual tracking
	\item Fully calibrate-able range measurements
	\item  
\end{itemize}

\chapter{Usage Instructions}
\section{Setup}
The Yavin 4 Defence System is designed to be self-initialising and require as little user setup as possible. Powering the system (by inserting a 9v battery, and pressing the on button), will start the system and put it into a default search/track mode. \newline
In the case of a non pre-assembled order, follow the following instructions to assemble the system \newline
\begin{enumerate}
	\item 
\end{enumerate}

\section{Interface}
The Yavin 4 Defence System can be operated from either a local mode, or a remote mode. Both interfaces are described below. By Default the system is in the local interface mode on start up.

\subsection{Local Mode}
In this mode the user input is entered through the manipulation of buttons and dials on the system.

\subsubsection{Layout}
<Include labelled pictures/diagrams of the local user interface here>

\subsection{Remote Mode}
in this mode all commands and inputs are sent to the system via RS-232 serial.

\subsubsection{Setup}
Usage of the remote mode requires only a generic serial terminal. The system does not require any specialist software, and is capable of running in any environment or system supporting RS-232.

\subsubsection{Layout}
<Include like example prompts etc, what the remote UI Looks like>

\subsubsection{Commands}
Below is a complete list of valid commands on the Yavin 4 Defence System, and their associated functions.

\begin{itemize}
	\item Esc - Exits a menu subsystem or cancels an action
	\item T - Start (or stop) automatic tracking
	\item Enter - Confirm action or enter submenu
	\item 1,2,3... - Select appropriate action or submenu
\end{itemize}

\section{Calibration}
Should you wish to calibrate any measurement on the Yavin 4 Defence System 

\chapter{Troubleshooting}

\end{document}          
